Continuous Generalization of Buildings \protect\\ by Growing and Merging

### 2017-08-30 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added figures/Shrink_Uniting.pdf

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{ErosionBreak}
	\caption{Dilate the gray polygon, then erode the dilated polygon.
		(a) Dilate and erode with distance $d_1$.
		(b) Dilate and erode with distance $d_2$, where $d_2>d_1$.
		In (a) the result of dilation and erosion is the same as the original 
		polygon, while in (b) the result consists of two parts.
	}
	\label{fig:ErosionBreak}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{ImaiIri_Shortcut}
	\caption{Valid and invalid shortcuts for Imai--Iri algorithm.}
	\label{fig:ImaiIri_Shortcut}
\end{figure}

@@

As we simplify buildings after growing, 
some parts of the buildings may shrink 
comparing to themselves at the immediate previous steps.
To avoid this shrink, we unite a building with itself at the immediate previous 
step so that the 
united building is always larger than both of the united parts.

>>>>

\newcommand{\blndraft}{true}
%\newcommand{\blndraft}{false}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=\blndraft]{ErosionBreak}
	\caption{Dilate the gray polygon, then erode the dilated polygon.
		(a) Dilate and erode with distance $d_1$.
		(b) Dilate and erode with distance $d_2$, where $d_2>d_1$.
		In (a) the result of dilation and erosion is the same as the original 
		polygon, while in (b) the result consists of two parts.
	}
	\label{fig:ErosionBreak}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=\blndraft]{ImaiIri_Shortcut}
	\caption{Valid and invalid shortcuts for Imai--Iri algorithm.}
	\label{fig:ImaiIri_Shortcut}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{Shrink_Uniting}
	\caption{Unite a polygon with the polygon at the immediately previous step.
		(a) Unite the polygon of \fig\ref{fig:Shrink_Erosion}~(c) and the 
		polygon of \fig\ref{fig:Shrink_Erosion}~(g);
		(b) Unite the polygon of \fig\ref{fig:Shrink_Simplification}~(c) and 
		the polygon of \fig\ref{fig:Shrink_Simplification}~(h);
	}
	\label{fig:Shrink_Uniting}
\end{figure}

As we simplify buildings after growing, 
some parts of the buildings may shrink 
comparing to themselves at the immediately previous steps.
To avoid this shrink, we unite a building with itself at the immediately 
previous 
step so that the 
united building is always larger than both of the united parts.
